\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-29 paper/eprv.tex
typo

\paragraph{Choice of template}
A variety of choices exist for the cross-correlation template
$f(v)$. A few possibilities include:
\begin{itemize}
\item \emph{A theoretically produced synthetic spectrum:}
  This will be a slightly wrong model prediction,
  since no stellar model will produce perfect reproduction of the
  spectral expectation for the star in question.
  The chosen template should be matched as closely as possible however
  to the target star. Some surveys cross correlate with one universal
  template for all stars; this will lead to increases in both bias and
  variance relative to the \CRLB.
\item \emph{A binary mask:}
  This is a or a spectrum of zero values with non-zero top-hats at the
  expected rest-frame wavelengths of the spectral lines of interest.
  A cross-correlation between this mask and the observed spectrum will
  effectively compute the average line profile with its minimum
  corresponding to the best-fit RV.
  As we note above, fitting that mean line profile with a Gaussian
  before identifying the \RV\ estimate is equivalent to smoothing the
  mask with a Gaussian and then using it as the stellar template in a
  straightforward cross correlation.
  The binary-mask method has the benefit of exactly zeroing out
  telluric-contaminated or otherwise unreliable regions of the
  spectrum (by deleting them from the mask).
  A desired relative weighting of lines can be incorporated by setting
  the non-zero mask values to different amplitudes at different lines
  (\CITE Pepe). This method is currently used by the \HARPS\ pipeline
  (\CITE), and an example is shown in \figurename~\ref{fig:binarymask}.
\item \emph{A data-driven estimate of the template spectrum:}
  Some surveys (for example, \HIRES, \CITE) use a single observation as a
  template.
  Combining information from many visits is better because the
  combined SNR will be higher.
  In what follows, we show that with sufficient epochs, a data-driven
  template is accurate enough to saturate the \CRLB.
\end{itemize}
\begin{figure}[htp]
\centering
% \includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window corresponds to the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}

>>>>

\paragraph{Choice of template}
A variety of choices exist for the cross-correlation template
$f(v)$. A few possibilities include:
\begin{itemize}
\item \emph{A theoretically produced synthetic spectrum:}
  This will be a slightly wrong model prediction,
  since no stellar model will produce perfect reproduction of the
  spectral expectation for the star in question.
  The chosen template should be matched as closely as possible however
  to the target star. Some surveys cross correlate with one universal
  template for all stars; this will lead to increases in both bias and
  variance relative to the \CRLB.
\item \emph{A binary mask:}
  This is a pseudo-spectrum of zero values with non-zero top-hats at the
  expected rest-frame wavelengths of the spectral lines of interest.
  A cross-correlation between this mask and the observed spectrum will
  effectively compute the average line profile with its minimum
  corresponding to the best-fit RV.
  As we note above, fitting that mean line profile with a Gaussian
  before identifying the \RV\ estimate is equivalent to smoothing the
  mask with a Gaussian and then using it as the stellar template in a
  straightforward cross correlation.
  The binary-mask method has the benefit of exactly zeroing out
  telluric-contaminated or otherwise unreliable regions of the
  spectrum (by deleting them from the mask).
  A desired relative weighting of lines can be incorporated by setting
  the non-zero mask values to different amplitudes at different lines
  (\CITE Pepe). This method is currently used by the \HARPS\ pipeline
  (\CITE), and an example is shown in \figurename~\ref{fig:binarymask}.
\item \emph{A data-driven estimate of the template spectrum:}
  Some surveys (for example, \HIRES, \CITE) use a single observation as a
  template.
  Combining information from many visits is better because the
  combined SNR will be higher.
  In what follows, we show that with sufficient epochs, a data-driven
  template is accurate enough to saturate the \CRLB.
\end{itemize}
\begin{figure}[htp]
\centering
% \includegraphics[width=\columnwidth]{binarymask}
\caption{Illustration of a weighted binary mask (blue windows) plotted over a small segment of the solar spectrum (black). The vertical length of each mask window corresponds to the weight given to the line when performing a cross-correlation between mask and spectrum.}
\label{fig:binarymask}
\end{figure}
